Continuous Deductive Reasoning over Streamed RDF Data

### 2015-11-03 article.tex
NEEDS WORK: referenced RSP community definition of streams, needs reason for using a subsumed semantics

WC-Datalog differs from conventional Datalog through the addition of
sources of continuously generated or reported facts (i.e streams), and
the application of windowing semantics over those sources,
thereby providing for the interpretation of WC-Datalog programs as
sequences of instantaneous states that may each be reduced to valid positive Datalog
programs.  As such, these states each inherit the semantics of
positive Datalog.  Furthermore, WC-Datalog provides for the continuous derivation
of entailments from this sequence of instantaneous states as a stream
of facts; these streams share a data model with the streams of
continuous queries, as defined by the stream processing community,
thereby allowing the integration of WC-Datalog programs into stream
processing pipelines. Finally, we show that these streams may be
manipulated to retrieve the instantaneous sets of entailments produced
by the equivalent Datalog programs.

>>>>

WC-Datalog differs from conventional Datalog through the addition of
sources of continuously generated or reported facts (i.e streams), and
the application of windowing semantics over those sources,
thereby providing for the interpretation of WC-Datalog programs as
sequences of instantaneous states that may each be reduced to valid positive Datalog
programs.  As such, these states each inherit the semantics of
positive Datalog.  Furthermore, WC-Datalog provides for the continuous derivation
of entailments from this sequence of instantaneous states as a stream
of facts; the data model of these streams is subsumed by that currently proposed
by the RDF stream processing community\footnote{As presented at
\url{https://github.com/streamreasoning/RSP-QL/blob/master/Semantics.md}
on \mbox{03/11/2015}.}, thereby allowing the integration of WC-Datalog programs
into stream processing pipelines. Finally, we show that these streams may be
manipulated to retrieve the instantaneous sets of entailments produced
by the equivalent Datalog programs.
